---
title: "Supporting Information 'Wildlife health perceptions and monitoring practices in globally distributed protected areas'"
author:
  - name: Diego Montecino-Latorre
    affiliations:
      - name: Wildlife Conservation Society - Health Program
        city: Bronx
        state: New York
  - name: Mathieu Pruvot
    affiliations:
      - name: Wildlife Conservation Society - Health Program
        city: Bronx
        state: New York
  - name: Sarah H Olson
    affiliations:
      - name: Wildlife Conservation Society - Health Program
        city: Bronx
        state: New York
number-sections: true
editor: visual
execute:
  cache: false
format: 
  html:
    self-contained: true
out-extra: 'style="margin-top:-20px;"'
opts_chunk:
    R.options:
    knitr.table.html.attr: "quarto-disable-processing=true"
code-link: false
---

```{r load packages}
#| echo: false
#| eval: true
#| message: false
#| warning: false

knitr::opts_chunk$set(fig.pos = "H", out.extra = "")

source("../R/load_packages.R")
```

```{r remove other audience answering the survey}
#| echo: false
#| eval: true
#| message: false
#| warning: false

terrestrial_data<-readRDS("../data/terrestrial_data.RDS")

# number_responses_before_audience_remove<-nrow(terrestrial_data)

#source("R/remove_other_audience.R")
terrestrial_data<-terrestrial_data %>% filter(position!="Other")

# number_responses_after_audience_remove<-nrow(terrestrial_data)

```

## Results of non-local responses

### Perceptions regarding wildlife health importance in conservation and potential consequences of pathogen transmission among wildlife, domestic animals, and people.

```{r perceptions regarding wildlife health importance in conservation and potential consequences of pathogen transmission among wildlife, domestic animals, and people}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| fig-width: 0.1
#| fig-height: 0.1

library(ggthemes)
library(grid)
library(patchwork)

section_1 =
  terrestrial_data %>% filter(local==F) %>% 
  select(#survey,
    wildlife_health_important,
    hum_liv_path_affect_wildlife,
    wildlife_path_affect_livestock,
    wildlife_path_affect_phealth)


section_1<-
  section_1 %>%
  #dplyr::select(-survey) %>%
  tidyr::pivot_longer(cols = everything()) %>%
  dplyr::group_by(name, value, .drop=FALSE) %>%
  dplyr::count(name,value) %>%
  dplyr::rename(c("question"="name", "rank"="value", "num_responses"="n")) %>%
  ungroup() %>%
  complete(question,rank,fill=list(num_responses=0)) %>%
  mutate(rank=factor(rank,
                     levels = rev(c("Strongly agree",
                                    "Agree",
                                    "Neutral",
                                    "Somewhat Disagree",
                                    "Disagree",
                                    "Strongly disagree")),
                     labels = rev(c("Strongly\nagree",
                                    "Agree",
                                    "Neutral",
                                    "Somewhat\ndisagree",
                                    "Disagree",
                                    "Strongly\ndisagree")))) %>%
  mutate(question=factor(question,
                         levels = rev(c("wildlife_health_important",
                                        "hum_liv_path_affect_wildlife",
                                        "wildlife_path_affect_phealth",
                                        "wildlife_path_affect_livestock")),
                         labels = rev(c("Wildlife health\nis important",
                                        "Human and livestock\npathogens can\nimpact wildlife\nhealth",
                                        "Wildlife pathogens can\nimpact human health",
                                        "Wildlife pathogens can\nimpact livestock health"))))


#Plot

likert_theme <-
  theme_wsj() +
  theme(text = element_text(size = 20),
        plot.title = element_text(size = 20, hjust = 0.5, 
                                  margin = margin(5, 0, 10, 0), family = "arial", face = "plain"),
        plot.margin = unit(c(0.2,0.2,0.2,0.2), "cm"),
        panel.grid = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size=16, face = "plain"),
        axis.ticks.x = element_line(colour = "black"),
        axis.ticks.y = element_line(colour = "black"),
        axis.title.y  = element_text(colour = "grey10", angle = 180, size=18, family = "arial"),
        axis.title.x  = element_text(colour = "grey10", size=18, family = "arial"),
        axis.line.y.right  = element_line(colour="black"),
        strip.text = element_text(colour="grey95", size = 18),
        strip.text.y.left = element_text(angle = 0, hjust = 0),
        legend.position = "none")

custom_colors<-c("Human and livestock\npathogens can\nimpact wildlife\nhealth" ="cornflowerblue", 
                 "Wildlife health\nis important" = "darkgreen" ,
                 "Wildlife pathogens can\nimpact livestock health" = "orange3", 
                 "Wildlife pathogens can\nimpact human health"="#ee6b6e")

section_1$dummy<-"a"

p<-
  ggplot(section_1, 
         aes(x = dummy, 
             y = num_responses,
             fill=question, 
             color=question, 
             alpha=rank)) +
  geom_bar(stat = "identity", position=position_dodge(width = 0.97), width=0.6) +
  #coord_flip()+
  facet_grid(question~rank, switch = "y")+
  scale_y_continuous(position = "right") +
  likert_theme +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm"),
        axis.line.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank()) +
  # facet_grid(name ~ found, scales = "free_x", space = "free_x", switch = "y") +
  scale_fill_manual(values = custom_colors) +
  scale_color_manual(values = custom_colors) +
  # scale_y_continuous(position = "right") +
  scale_alpha_discrete(range = c(0.3, 1)) +  # Set min and max alpha values
  ggtitle("Agreement ranking") +
  labs(y = "Number of responses\n")






# Generate the ggplot2 plot grob
g <- grid.force(ggplotGrob(p))
# Get the names of grobs and their gPaths into a data.frame structure
grobs_df <- do.call(cbind.data.frame, grid.ls(g, print = FALSE))
# Build optimal gPaths that will be later used to identify grobs and edit them
grobs_df$gPath_full <- paste(grobs_df$gPath, grobs_df$name, sep = "::")
grobs_df$gPath_full <- gsub(pattern = "layout::", 
                            replacement = "", 
                            x = grobs_df$gPath_full, 
                            fixed = TRUE)

# Get the gPaths of the strip background grobs
strip_bg_gpath <- grobs_df$gPath_full[grepl(pattern = ".*strip\\.background.*", 
                                            x = grobs_df$gPath_full)]
# strip_bg_gpath[1] # example of a gPath for strip background 
## [1] "strip-t-1.7-5-7-5::strip.1-1-1-1::strip.background.x..rect.5374"

# Get the gPaths of the strip titles
strip_txt_gpath <- grobs_df$gPath_full[grepl(pattern = "strip.*titleGrob.*text.*",
                                             x = grobs_df$gPath_full)]
# strip_txt_gpath[1] # example of a gPath for strip title
## [1] "strip-t-1.7-5-7-5::strip.1-1-1-1::GRID.titleGrob.5368::GRID.text.5364"

#Now we can edit the grobs:

# Generate some color
# n_cols <- length(strip_bg_gpath[1:7])
# fills <- rainbow(n_cols)
#bkg_colors1 <- RColorBrewer::brewer.pal(n = 9, name = "Greys")[3:9]
bkg_colors1 <- paste0("grey",seq(from=80, to=10, by=-13))
bkg_colors2 <- c("orange3", "#ee6b6e", "cornflowerblue", "darkgreen")

# Edit the grobs
# for (i in 1:length(strip_bg_gpath)){
# for (i in 1:7){
#   #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
#    g <- editGrob(grob = g, gPath = strip_txt_gpath[i], gp = gpar(col = txt_colors1[i]))
# }

for (i in 1:6){
  #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
  g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = bkg_colors1[i]))
}

for (i in 7:10){
  #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
  g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = bkg_colors2[i-6]))
}


# for (i in 8:10){
#   #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
#   g <- editGrob(grob = g, gPath = strip_txt_gpath[i], gp = gpar(col = txt_colors2[i-7]))
# }


# Draw the edited plot
# grid.newpage(); 
# grid.draw(g)

g<-ggpubr::as_ggplot(g)

# Create a single y-axis title as a separate plot
y_title <- ggplot() + 
  likert_theme +
  theme(panel.background = element_rect(fill = "#F7F2E6", colour = NA),
        plot.title = element_text(size = 20, hjust = 0.5, 
                                  margin = margin(0, 0, 0, 0), family = "arial", face = "plain"),
        plot.margin = unit(c(0,0,0,0), "cm"),
        plot.background = element_rect(fill ="#F7F2E6", colour = NA),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x  = element_blank(),
        axis.ticks.y  = element_blank(),
        axis.line.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y= element_blank()) +
  
  geom_text(aes(x = 0.5, y = 0.5), label = "Item             ", angle = 90, size = 7) 

# y_title

# Combine the y-axis title and the plot using patchwork
mix <- y_title + g + plot_layout(widths = c(1, 15))  # Adjust widths as needed
mix <- mix + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))



# if(!file.exists("../SMART_survey/plots/plot_section_1.png")) {

# ggsave(plot = mix, filename = "v2/plot_1.png", width = 12.85714, height = 9, dpi=300)

```

```{r section 1 plot}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| out-extra: 'style="margin-top:0px;"'
#| fig-width: 12.85714
#| fig-height: 9
#| fig-align: center
#| fig-cap: Figure S1. Distribution of the level of agreement (grey scale) among non-local protected area data managers with statements 'Pathogens carried by wildlife inhabiting the protected area(s) where I work in can affect livestock health’ (brown), ‘Pathogens carried by wildlife inhabiting the protected area(s) where I work in can affect human health' (red), ‘Human or livestock pathogens can affect wildlife populations inhabiting the protected area(s) where I work in’ (blue), and ‘Wildlife health is important to achieve the conservation goals of the protected area(s) where I work’ (green).


mix
```

### Overall frequency of encounters with dead, sick, or injured wildlife in protected areas and their documentation when found during patrols

```{r Overall frequency of encounters with dead, sick, or injured wildlife in protected areas and their documentation when found during patrols}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| fig-width: 0.1
#| fig-height: 0.1

library(ggthemes)
library(grid)
library(patchwork)

section_2 <-
  terrestrial_data |> filter(local==F) |> 
  select(dead_found,
         sick_injured_found,
         dead_wl_recorded,
         sick_wl_recorded,
         injured_wl_recorded)



dead_found_recorded<-
  section_2 |>
  # dplyr::select(-survey) |>
  dplyr::count(dead_found, dead_wl_recorded, name = "total_dead_found_recorded_group") |> 
  # tidyr::complete(dead_found, dead_wl_recorded ) |> 
  tidyr::replace_na(replace = list(total_dead_found_recorded_group=0)) #|> 

sick_found_recorded<-
  section_2 |>
  # dplyr::select(-survey) |>
  dplyr::count(sick_injured_found, sick_wl_recorded, name = "total_sick_found_recorded_group") |> 
  # tidyr::complete(sick_injured_found, sick_wl_recorded ) |> 
  tidyr::replace_na(replace = list(total_sick_found_recorded_group=0)) #|> 

injured_found_recorded<-
  section_2 |>
  # dplyr::select(-survey) |>
  dplyr::count(sick_injured_found, injured_wl_recorded, name = "total_injured_found_recorded_group") |> 
  # tidyr::complete(sick_injured_found, injured_wl_recorded ) |> 
  tidyr::replace_na(replace = list(total_injured_found_recorded_group=0)) #|> 







freq_found_recorded<-full_join(
  dead_found_recorded, 
  sick_found_recorded, 
  by = c("dead_found" = "sick_injured_found",
         "dead_wl_recorded" = "sick_wl_recorded")) 

freq_found_recorded<-
  full_join(
    freq_found_recorded, 
    injured_found_recorded, 
    by = c("dead_found" = "sick_injured_found",
           "dead_wl_recorded" = "injured_wl_recorded")) |> 
  rename(found = dead_found) |> 
  rename(recorded=dead_wl_recorded) |> 
  rename(dead=total_dead_found_recorded_group) |> 
  rename(sick=total_sick_found_recorded_group) |>
  rename(injured=total_injured_found_recorded_group) |> 
  mutate(found=factor(found,
                      levels = rev(c("Always",
                                     "Very frequently",
                                     "Occasionally",
                                     "Sometimes",
                                     "Rarely",
                                     "Very rarely",
                                     "Never")),
                      labels = rev(c("Always",
                                     "Very\nfrequently",
                                     "Occasionally",
                                     "Sometimes",
                                     "Rarely",
                                     "Very\nrarely",
                                     "Never"))))


freq_found_recorded<-
  freq_found_recorded |>  
  tidyr::pivot_longer(cols=c("dead", "sick", "injured")) |> 
  arrange(found) |> 
  mutate(name=factor(name, 
                     levels = c("injured", "sick", "dead"),
                     labels = c("Injured*",
                                "Sick*",
                                "Dead"))) 

freq_found_recorded<-
freq_found_recorded |> 
  tidyr::complete( found, recorded, name) |> 
  tidyr::replace_na(replace = list(value=0)) #|> 


freq_found_recorded<-
  freq_found_recorded |> 
  group_by(name, found) |> 
  mutate(prop = value/sum(value))

likert_theme <-
  # theme_gray() + 
  theme_wsj() +
  theme(text = element_text(size = 20),
        plot.title = element_text(size = 20, hjust = 0.5, 
                                  margin = margin(5, 0, 10, 0), family = "arial", face = "plain"),
        plot.margin = unit(c(0.2,0.2,0.2,0.2), "cm"),
        #plot.margin = unit(c(2.4,0,2.4,.4), "cm"),
        # plot.background = element_rect(linewidth = 2, color = "black"),
        panel.grid = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #axis.text.x = element_blank(),
        axis.text = element_text(size=16, face = "plain"),
        axis.ticks.x = element_line(colour = "black"),
        axis.ticks.y = element_line(colour = "black"),
        axis.title.y  = element_text(colour = "grey10", angle = 180, size=18, family = "arial"),
        axis.title.x  = element_text(colour = "grey10", size=18, family = "arial"),
        #panel.background = element_blank(),
        #strip.background  = element_blank(),
        axis.line.y.right  = element_line(colour="black"),
        strip.text = element_text(colour="grey95", size = 18),
        #strip.text.x = element_text(colour="grey75"),
        strip.text.y.left = element_text(angle = 0, hjust = 0),
        legend.position = "none")


freq_found_recorded<-
  freq_found_recorded |>
  mutate(transparency=if_else(recorded=="No", 0.4,1))


# camcorder::gg_resize_film( height = 2.2/2*3,
#                            width = 6.4,
#                            units = "in")



# Create a new column combining `recorded` and `name` for unique colors
freq_found_recorded$combined <- with(freq_found_recorded, paste(recorded, name, sep = "_"))

custom_colors <- c(
  "No_Dead" = "#1f77b4",    # Blue for No - Dead wildlife
  "Yes_Dead" = "navyblue",   # Orange for Yes - Dead wildlife
  "No_Sick*" = "pink",   # Green for No - Sick wildlife
  "Yes_Sick*" = "#d62728",  # Red for Yes - Sick wildlife
  "No_Injured*" = "orange", # Purple for No - Injured wildlife
  "Yes_Injured*" = "orange3" # Brown for Yes - Injured wildlife
)

p<-
  ggplot(freq_found_recorded, 
         aes(x = recorded, 
             y = value, 
             fill = combined, 
             color = combined, 
             alpha=as.numeric(found))) +
  likert_theme +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  geom_bar(stat = "identity", position=position_dodge(width = 0.97)) +
  geom_bar(aes(y = prop*100/5,
               x = recorded), 
           stat="identity", 
           width = 0.2, 
           position = position_nudge(x = 0.6), 
           fill=ifelse(freq_found_recorded$recorded=="No", NA, "darkgreen"),
           colour=ifelse(freq_found_recorded$recorded=="No", NA, "darkgreen")) +
  facet_grid(name ~ found, scales = "free_x", space = "free_x", switch = "y") +
  scale_fill_manual(values = custom_colors) +
  scale_color_manual(values = custom_colors) +
  scale_y_continuous(position = "right") +
  scale_alpha_continuous(range = c(0.3, 1)) +  # Set min and max alpha values
  ggtitle("Overall encounter frecuency in protected area(s)") +
  labs(x = "\nRecording", y = "Number of responses\n")



# Generate the ggplot2 plot grob
g <- grid.force(ggplotGrob(p))
# Get the names of grobs and their gPaths into a data.frame structure
grobs_df <- do.call(cbind.data.frame, grid.ls(g, print = FALSE))
# Build optimal gPaths that will be later used to identify grobs and edit them
grobs_df$gPath_full <- paste(grobs_df$gPath, grobs_df$name, sep = "::")
grobs_df$gPath_full <- gsub(pattern = "layout::", 
                            replacement = "", 
                            x = grobs_df$gPath_full, 
                            fixed = TRUE)

# Get the gPaths of the strip background grobs
strip_bg_gpath <- grobs_df$gPath_full[grepl(pattern = ".*strip\\.background.*", 
                                            x = grobs_df$gPath_full)]
# strip_bg_gpath[1] # example of a gPath for strip background 
## [1] "strip-t-1.7-5-7-5::strip.1-1-1-1::strip.background.x..rect.5374"

# Get the gPaths of the strip titles
strip_txt_gpath <- grobs_df$gPath_full[grepl(pattern = "strip.*titleGrob.*text.*",
                                             x = grobs_df$gPath_full)]
# strip_txt_gpath[1] # example of a gPath for strip title
## [1] "strip-t-1.7-5-7-5::strip.1-1-1-1::GRID.titleGrob.5368::GRID.text.5364"

#Now we can edit the grobs:

# Generate some color
# n_cols <- length(strip_bg_gpath[1:7])
# fills <- rainbow(n_cols)
#bkg_colors1 <- RColorBrewer::brewer.pal(n = 9, name = "Greys")[3:9]
bkg_colors1 <- paste0("grey",seq(from=80, to=10, by=-11))
bkg_colors2 <- c("orange3", "#ee6b6e", "cornflowerblue")

# Edit the grobs
# for (i in 1:length(strip_bg_gpath)){
# for (i in 1:7){
#   #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
#    g <- editGrob(grob = g, gPath = strip_txt_gpath[i], gp = gpar(col = txt_colors1[i]))
# }

for (i in 1:7){
  #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
  g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = bkg_colors1[i]))
}

for (i in 8:10){
  #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
  g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = bkg_colors2[i-7]))
}


# for (i in 8:10){
#   #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
#   g <- editGrob(grob = g, gPath = strip_txt_gpath[i], gp = gpar(col = txt_colors2[i-7]))
# }


# Draw the edited plot
# grid.newpage(); 
# grid.draw(g)

g<-ggpubr::as_ggplot(g)

# Create a single y-axis title as a separate plot
y_title <- ggplot() + 
  likert_theme +
  theme(panel.background = element_rect(fill = "#F7F2E6", colour = NA),
        plot.title = element_text(size = 20, hjust = 0.5, 
                                  margin = margin(0, 0, 0, 0), family = "arial", face = "plain"),
        plot.margin = unit(c(0,0,0,0), "cm"),
        plot.background = element_rect(fill ="#F7F2E6", colour = NA),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x  = element_blank(),
        axis.ticks.y  = element_blank(),
        axis.line.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y= element_blank()) +
  
  geom_text(aes(x = 0.5, y = 0.5), label = "Wildlife category", angle = 90, size = 7) 

# Combine the y-axis title and the plot using patchwork
mix <- y_title + g + plot_layout(widths = c(1, 15))  # Adjust widths as needed
mix2 <- mix + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))

```

```{r section 2 plot}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| fig-align: center
#| fig-height: 9
#| fig-width: 15
#| fig-cap: Figure S2. Distribution of non-local protected area data manager responses regarding the encounter of or injured (brown), sick (red), dead (blue) wildlife in the protected area(s) where they work and the recording (bright color) or non-recoding (pale color) of these animals when encountered. Green bars represent the proportion of responses that reported the recording of wildlife per wildlife category and encounter frequency.  

mix2

```

```{r section 2 table}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| fig-align: center
#| fig-height: 3.2
#| fig-cap: Table S1. Distribution of the method of documentation to register either healthy, sick, injured, or dead wildlife found during ranger patrols reported by non-local protected area data managers ('Individual observation', 'Part of the full count', 'Present or absent', 'Another way') and the recording of specific data items for each wildlife health status across documentation methods. 


# Create dataset for the table

source("bar_chart_in_gt.R")
library(ggthemes)
library(grid)
library(paletteer)
library(gt)


collapse_rows_gt<-source("https://gist.githubusercontent.com/jmclawson/6852c14023d7d9b7e91bbcfa419adeb8/raw/7435c51c05ff5f537bd545c63325ea2ed4681a91/collapse_rows.R")

collapse_rows_gt<-collapse_rows_gt$value

source("create_datasets_for_table_1.R")


#healthy dataset
healthy<-create_status_tibble(status="healthy")

healthy<-
  healthy |> 
  mutate(across(where(is.double), ~replace_na(., 0))) |> 
  rename("how_wl_recorded" = "how_healthy_wl_recorded") |> 
  rename("condition" = "body_condition")|> 
  arrange(how_wl_recorded)



#injured dataset
injured<-create_status_tibble(status="injured")

injured<-
  injured |> 
  mutate(across(where(is.double), ~replace_na(., 0))) |>   # Replace NA with 0 for double columns
  rename("anomalies" ='anomalies_signs_if_any') |> 
  rename("suspected_cause" = contains("suspect_cause")) |> 
  rename("how_wl_recorded" = "how_injured_wl_recorded") |> 
  rename("condition" = "body_condition")|> 
  arrange(how_wl_recorded)



#sick dataset
sick<-create_status_tibble(status="sick")

sick<-
  sick |> 
  mutate(across(where(is.double), ~replace_na(., 0))) |>   # Replace NA with 0 for double columns
  rename("anomalies" ='anomalies_signs_if_any') |> 
  rename("suspected_cause" = contains("suspect_cause")) |> 
  rename("how_wl_recorded" = "how_sick_wl_recorded") |> 
  rename("condition" = "body_condition")|> 
  arrange(how_wl_recorded)





#dead dataset

# terrestrial_data |> 
#   select(contains("dead")) |> 
#   filter(dead_wl_recorded=="Yes") |> 
#   count(how_dead_wl_recorded)

dead<-create_status_tibble(status="dead")

dead<-
  dead |> 
  mutate(across(where(is.double), ~replace_na(., 0))) |>   # Replace NA with 0 for double columns
  rename("anomalies" ='anomalies_in_carcass_if_any') |> 
  rename("suspected_cause" = contains("suspect_cause")) |> 
  rename("how_wl_recorded" = "how_dead_wl_recorded") |> 
  rename("condition" = "carcass_condition") |> 
  arrange(how_wl_recorded)



full_data<-
  full_join(healthy, injured) |> 
  full_join(sick) |> 
  full_join(dead) 


number_recording_healthy<-
  terrestrial_data |> 
  filter(local == FALSE) |> 
  count(healthy_wl_recorded) |> 
  filter(healthy_wl_recorded=="Yes") |> 
  pull(n)

number_recording_injured<-
  terrestrial_data |> 
  filter(local == FALSE) |> 
  count(injured_wl_recorded) |> 
  filter(injured_wl_recorded=="Yes") |> 
  pull(n)


number_recording_sick<-
  terrestrial_data |> 
  filter(local == FALSE) |> 
  count(sick_wl_recorded) |> 
  filter(sick_wl_recorded=="Yes") |> 
  pull(n)


number_recording_dead<-
  terrestrial_data |> 
  filter(local == FALSE) |> 
  count(dead_wl_recorded) |> 
  filter(dead_wl_recorded=="Yes") |> 
  pull(n)


number_recording_at_least_one_non_healthly_cat<-
  terrestrial_data |> 
  filter(local == FALSE) |> 
  filter(sick_wl_recorded=="Yes" | injured_wl_recorded=="Yes" | dead_wl_recorded=="Yes") |> 
  select(sick_wl_recorded, 
         injured_wl_recorded,
         dead_wl_recorded) |> 
  nrow()


full_data[full_data$status=="Healthy",]$status<-paste0("Healthy (n = ", number_recording_healthy, ")")
full_data[full_data$status=="Injured",]$status<-paste0("Injured (n = ", number_recording_injured, ")")
full_data[full_data$status=="Sick",]$status<-paste0("Sick (n = ", number_recording_sick, ")")
full_data[full_data$status=="Dead",]$status<-paste0("Dead (n = ", number_recording_dead, ")")




## TABLES ##




prop_how_recorded_colors<-
  purrr::map(c("#000080", "#d62728", "#C76E00", "#06402B"), \(x) rep(x, 4)) |> unlist() |> rev()

prop_what_recorded_colors<-
  purrr::map(c("#1f77b4", "pink", "orange", "#ABDDA4"), \(x) rep(x, 4)) |> unlist() |> rev()



full_table<-
  full_data |> 
  mutate(
    prop_how_recorded = 
      purrr::map2_chr(.x = full_data$prop_how_recorded*100, 
                      .y = prop_how_recorded_colors, .f = 
                        ~bar_chart(label = .x, 
                                   fill = .y, 
                                   background = "#d2d2d2")) |> 
      purrr::map(gt::html),
    
    species = purrr::map2_chr(.x = full_data$species*100, 
                              .y = prop_what_recorded_colors, .f = 
                                ~bar_chart(label = .x, 
                                           fill = .y, 
                                           background = "#d2d2d2")) |> 
      purrr::map(gt::html),
    
    
    age = purrr::map2_chr(.x = full_data$age*100, 
                          .y = prop_what_recorded_colors, .f = 
                            ~bar_chart(label = .x, 
                                       fill = .y, 
                                       background = "#d2d2d2")) |> 
      purrr::map(gt::html),
    
    sex = purrr::map2_chr(.x = full_data$sex*100, 
                          .y = prop_what_recorded_colors, .f = 
                            ~bar_chart(label = .x, 
                                       fill = .y, 
                                       background = "#d2d2d2")) |> 
      purrr::map(gt::html),
    
    condition = purrr::map2_chr(.x = full_data$condition*100, 
                                .y = prop_what_recorded_colors, .f = 
                                  ~bar_chart(label = .x, 
                                             fill = .y, 
                                             background = "#d2d2d2")) |> 
      purrr::map(gt::html),
    
    anomalies = purrr::map2_chr(.x = full_data$anomalies*100, 
                                .y = prop_what_recorded_colors, .f = 
                                  ~bar_chart(label = .x, 
                                             fill = .y, 
                                             background = "#d2d2d2")) |> 
      purrr::map(gt::html),
    
    photographs = purrr::map2_chr(.x = full_data$photographs*100, 
                                  .y = prop_what_recorded_colors, .f = 
                                    ~bar_chart(label = .x, 
                                               fill = .y, 
                                               background = "#d2d2d2")) |> 
      purrr::map(gt::html),
    
    other = purrr::map2_chr(.x = full_data$other*100, 
                            .y = prop_what_recorded_colors, .f = 
                              ~bar_chart(label = .x, 
                                         fill = .y, 
                                         background = "#d2d2d2")) |> 
      purrr::map(gt::html)) %>% 
  dplyr::select(
    status,
    how_wl_recorded,
    prop_how_recorded, 
    species,
    age,
    sex,
    condition,
    anomalies,
    photographs,
    other) %>%
  gt() |> 
  cols_align(align = "left") |> 
  cols_label(
    status = "Wildlife<br>category",
    species = "Species",
    age = "Age",
    sex = "Sex", 
    condition = "Condition",
    anomalies = "Anomalies",
    photographs = "Photographs",
    other = "Other",
    .fn = md) |> 
  tab_spanner(label = md("**Documentation method used (%)**"),
              columns = c(how_wl_recorded,
                          prop_how_recorded)) |> 
  tab_spanner(label = md("**Data items recorded (%)**"),
              columns = c(species,
                          age,
                          sex,
                          condition,
                          anomalies,
                          photographs,
                          other)) |>
  cols_label(
    how_wl_recorded = "",
    prop_how_recorded = "") |> 
  cols_width(everything() ~ px(140)) |> 
  collapse_rows_gt(status)


fix_anomalies_for_healthy<-gt::html("<div style='display:flex;align-items:left;'><div style='position:relative;flex-grow:1;margin-left:8px;background:white;'><div style='position:absolute;width:0;height:30px;border-left:2px solid white;left:50%;top:0;'></div><div style='background:white;width:NA%;height:30px;'></div></div></div>")
full_table$`_data`$anomalies[[1]]<-fix_anomalies_for_healthy
full_table$`_data`$anomalies[[2]]<-fix_anomalies_for_healthy
full_table$`_data`$anomalies[[3]]<-fix_anomalies_for_healthy
full_table$`_data`$anomalies[[4]]<-fix_anomalies_for_healthy

# test<-as_gtable(full_table)
# library(patchwork)
# wrap_elements(full_table)
#   
# patchwork::wrap_ggplot_grob(full_table)
# 
# class(full_table)
# test<-gtExtras::gt_reprex_image(full_table)
# gtExtras::gtsave_extra(full_table, "v2/table1.png")
# 
# gtsave(full_table, "v2/table1.rtf")
# png("v2/table1.png", width = 10, height = 7, units = 'in', res = 300)

full_table



```

### Presence of domestic animals in protected areas, the documentation of their health status, and the perceived threats of domestic animals to conservation goals

```{r Presence of domestic animals in protected areas, the documentation of their health status, and the perceived threats of domestic animals to conservation goals}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| fig-width: 0.1
#| fig-height: 0.1


section_3 <-
  terrestrial_data |> filter(local==T) |> 
  select(dom_animals_concern,
         dom_animals_in_pa,
         dom_animals_recorded,
         dom_animal_health_status_recorded)

section_3<-section_3  %>% 
  mutate(dom_animals_concern=factor(dom_animals_concern,
                                    levels = rev(c("Strongly agree",
                                                   "Agree",
                                                   "Neutral",
                                                   "Somewhat Disagree",
                                                   "Disagree",
                                                   "Strongly disagree")),
                                    labels = rev(c("Strongly\nagree",
                                                   "Agree",
                                                   "Neutral",
                                                   "Somewhat\ndisagree",
                                                   "Disagree",
                                                   "Strongly\ndisagree"))))



dom_found_recorded<-
  section_3 |>
  dplyr::add_count(dom_animals_concern, 
                   dom_animals_recorded, 
                   dom_animal_health_status_recorded,
                   name = "n_concern_dom_animals_recorded") |> 
  tidyr::complete(dom_animals_concern, dom_animals_in_pa, dom_animals_recorded) |> 
  dplyr::filter(!(dom_animals_in_pa=="No" & dom_animals_recorded!="")) |> 
  dplyr::filter(!(dom_animals_in_pa=="Yes" & dom_animals_recorded=="")) 

# dom_found_recorded |> arrange(dom_animals_concern)

dom_found_recorded[which(
  dom_found_recorded$dom_animals_concern=="Strongly\ndisagree" &
    dom_found_recorded$dom_animals_in_pa=="Yes"),]$n_concern_dom_animals_recorded<-0

# dom_found_recorded<-
# dom_found_recorded |> 
#   filter(!is.na(dom_animals_concern))

dom_found_recorded[dom_found_recorded$dom_animals_recorded=="",]$dom_animals_recorded<-"NA"


# dplyr::mutate(
#   n_concern_dom_animals_recorded=
#     if_else(dom_animals_recorded=="",
#             NA,
#             n_concern_dom_animals_recorded))
# 

# Create a new column combining `recorded` and `name` for unique colors
dom_found_recorded$combined <- 
  with(dom_found_recorded, 
       paste(dom_animals_in_pa, 
             dom_animals_recorded, 
             dom_animal_health_status_recorded, 
             sep = "_"))

custom_colors <- c(
  "No_NA_NA" = "#d62728",
  "No_NA_" = "#d62728",
  "Yes_No_" =  "cornflowerblue",
  "Yes_No_NA" = "cornflowerblue",
  "Yes_Yes_NA" = "blue",
  "Yes_Yes_No" = "blue",
  "Yes_Yes_Yes" = "navyblue")

dom_found_recorded<-
  dom_found_recorded |> distinct()

dom_found_recorded$n_concern_dom_animals_recorded[
  is.na(dom_found_recorded$n_concern_dom_animals_recorded) &
    dom_found_recorded$combined=="No_NA_NA"]<-0

dom_found_recorded$n_concern_dom_animals_recorded[
  dom_found_recorded$dom_animals_concern=="Neutral" &
  dom_found_recorded$dom_animals_recorded=="No"]<-0

# Plot 

likert_theme <-
  # theme_gray() + 
  theme_wsj() +
  theme(text = element_text(size = 20),
        plot.title = element_text(size = 20, hjust = 0.5, 
                                  margin = margin(5, 0, 10, 0), family = "arial", face = "plain"),
        plot.margin = unit(c(0.2,0.2,0.2,0.2), "cm"),
        #plot.margin = unit(c(2.4,0,2.4,.4), "cm"),
        # plot.background = element_rect(linewidth = 2, color = "black"),
        panel.grid = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #axis.text.x = element_blank(),
        axis.text = element_text(size=16, face = "plain"),
        axis.ticks.x = element_line(colour = "black"),
        axis.ticks.y = element_line(colour = "black"),
        axis.title.y  = element_text(colour = "grey10", angle = 180, size=18, family = "arial"),
        axis.title.x  = element_text(colour = "grey10", size=18, family = "arial"),
        #panel.background = element_blank(),
        #strip.background  = element_blank(),
        axis.line.y.right  = element_line(colour="black"),
        strip.text = element_text(colour="grey95", size = 18),
        #strip.text.x = element_text(colour="grey75"),
        strip.text.y.left = element_text(angle = 0, hjust = 0),
        legend.position = "none")

p<-
  ggplot(dom_found_recorded , 
         aes(x = dom_animals_recorded, 
             y = n_concern_dom_animals_recorded,
             fill = combined,
             colour = combined,
             alpha = as.numeric(dom_animals_concern))) +
  geom_bar(stat = "identity", position="stack", width = 0.97) +
  #facet_grid(.~dom_animals_concern, switch = "y")
  facet_grid(dom_animals_in_pa~dom_animals_concern, 
             scales = "free_x", 
             space = "free_x", switch = "y") +
  scale_fill_manual(values = custom_colors) +
  scale_color_manual(values = custom_colors) +
  likert_theme +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  scale_y_continuous(position = "right") +
  scale_alpha_continuous(range = c(0.3, 0.9)) +  # Set min and max alpha values
  ggtitle("Overall agreement domestic animals are a conservation concern") +
  labs(x = "\nRecording", y = "Number of responses\n")

# p

# Generate the ggplot2 plot grob
g <- grid.force(ggplotGrob(p))
# Get the names of grobs and their gPaths into a data.frame structure
grobs_df <- do.call(cbind.data.frame, grid.ls(g, print = FALSE))
# Build optimal gPaths that will be later used to identify grobs and edit them
grobs_df$gPath_full <- paste(grobs_df$gPath, grobs_df$name, sep = "::")
grobs_df$gPath_full <- gsub(pattern = "layout::", 
                            replacement = "", 
                            x = grobs_df$gPath_full, 
                            fixed = TRUE)

# Get the gPaths of the strip background grobs
strip_bg_gpath <- grobs_df$gPath_full[grepl(pattern = ".*strip\\.background.*", 
                                            x = grobs_df$gPath_full)]
# strip_bg_gpath[1] # example of a gPath for strip background 
## [1] "strip-t-1.7-5-7-5::strip.1-1-1-1::strip.background.x..rect.5374"

# Get the gPaths of the strip titles
strip_txt_gpath <- grobs_df$gPath_full[grepl(pattern = "strip.*titleGrob.*text.*",
                                             x = grobs_df$gPath_full)]
# strip_txt_gpath[1] # example of a gPath for strip title
## [1] "strip-t-1.7-5-7-5::strip.1-1-1-1::GRID.titleGrob.5368::GRID.text.5364"

#Now we can edit the grobs:

# Generate some color
# n_cols <- length(strip_bg_gpath[1:7])
# fills <- rainbow(n_cols)
#bkg_colors1 <- RColorBrewer::brewer.pal(n = 9, name = "Greys")[3:9]
bkg_colors1 <- paste0("grey",seq(from=80, to=10, by=-13))
bkg_colors2 <- c("#ee6b6e", "cornflowerblue")


for (i in 1:6){
  #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
  g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = bkg_colors1[i]))
}

for (i in 7:8){
  #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
  g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = bkg_colors2[i-6]))
}


# for (i in 8:10){
#   #g <- editGrob(grob = g, gPath = strip_bg_gpath[i], gp = gpar(fill = fills[i-7]))
#   g <- editGrob(grob = g, gPath = strip_txt_gpath[i], gp = gpar(col = txt_colors2[i-7]))
# }


# Draw the edited plot
# grid.newpage(); 
# grid.draw(g)

g<-ggpubr::as_ggplot(g)

# Create a single y-axis title as a separate plot
y_title <- ggplot() + 
  likert_theme +
  theme(panel.background = element_rect(fill = "#F7F2E6", colour = NA),
        plot.title = element_text(size = 20, hjust = 0.5, 
                                  margin = margin(0, 0, 0, 0), family = "arial", face = "plain"),
        plot.margin = unit(c(0,0,0,0), "cm"),
        plot.background = element_rect(fill ="#F7F2E6", colour = NA),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x  = element_blank(),
        axis.ticks.y  = element_blank(),
        axis.line.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y= element_blank()) +
  
  geom_text(aes(x = 0.5, y = 0.5), 
            label = "Domestic animals in protected area    ", 
            angle = 90, 
            size = 7) 

# y_title
  
# Combine the y-axis title and the plot using patchwork
mix <- y_title + g + plot_layout(widths = c(1, 15))  # Adjust widths as needed
mix3 <- mix + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))

```

<div style="margin-top:0px;">

```{r plot section 3}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| fig-height: 6
#| fig-width: 12.85714
#| fig-align: center
#| fig-cap: Figure S3. Distribution of the level of agreement among non-local protected area data managers with the statement 'Introduced domestic animals (e.g., dogs, cats, cattle, pigs, cows) are a concern for the conservation goals of the protected areas where I work' for the groups that reported the absence (red) and presence (blue) of domestic animals in the protected area(s) and their recording in the latter. Darker segments in the bars at the “Yes recording of domestic animals” category (x-axis) represent the number of responses that documented domestic animal health status.

mix3

```

## Distribution of responses across their overall agreement with 'human and livestock pathogens can impact wildlife health' and 'introduced domestic animals are a concern for the conservation goals of the protected area'

```{r section 0.1 plot}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| fig-height: 3.5
#| fig-align: center
#| fig-cap: Figure S4. Distribution of protected area data managers responses across their overall agreement with 'human and livestock pathogens can impact wildlife health' and 'introduced domestic animals are a concern for the conservation goals of the protected area' for those protected area managers that reported the absence of domestic animals in the protected area.

dom_animals<-
  terrestrial_data %>% 
  # filter(local==T) %>% 
  select(
    dom_animals_concern,
    dom_animals_in_pa,
    dom_animals_recorded,
    dom_animal_health_status_recorded,
    wildlife_path_affect_livestock,
    hum_liv_path_affect_wildlife
    ) #%>% 

dom_animals<-
  dom_animals %>% 
  count(dom_animals_concern,
        hum_liv_path_affect_wildlife,
        dom_animals_in_pa, name = "value") %>% 
        #dom_animals_recorded, #name = "value") %>% 
        #dom_animal_health_status_recorded, name = "value") %>% 
  complete(dom_animals_in_pa,
           dom_animals_concern,
           hum_liv_path_affect_wildlife,
                   #dom_animals_recorded,
                   #dom_animal_health_status_recorded),
           fill = list(value = 0))


dom_animals <- dom_animals  %>% 
  mutate(dom_animals_concern=factor(dom_animals_concern,
                                    levels = c("Strongly agree",
                                                   "Agree",
                                                   "Neutral",
                                                   "Somewhat Disagree",
                                                   "Disagree",
                                                   "Strongly disagree"),
                                    labels = c("Strongly\nagree",
                                                   "Agree",
                                                   "Neutral",
                                                   "Somewhat\ndisagree",
                                                   "Disagree",
                                                   "Strongly\ndisagree"))) %>% 
  mutate(hum_liv_path_affect_wildlife=factor(hum_liv_path_affect_wildlife,
                                    levels = c("Strongly agree",
                                               "Agree",
                                               "Neutral",
                                               "Somewhat Disagree",
                                               "Disagree",
                                               "Strongly disagree"),
                                    labels = c("Strongly\nagree",
                                               "Agree",
                                               "Neutral",
                                               "Somewhat\ndisagree",
                                               "Disagree",
                                               "Strongly\ndisagree"))) 


dom_animals <- dom_animals %>% 
  group_by(dom_animals_in_pa) %>% 
  arrange(dom_animals_concern) %>% 
  # print(n = 50) %>% 
  group_split()



likert_theme <-
  theme_gray() +
  theme(text = element_text(size = 12),
        plot.title = element_text(size = 13, hjust = 0.5, 
                                  margin = margin(0, 0, 0, 0)),
        plot.margin = unit(c(0.5,0.5,0.2,0.5), "cm"),
        plot.background = element_rect(linewidth = 1, color = "black"),
        panel.grid = element_blank(),
        axis.text = element_text(size = 8),
        # axis.text.y = element_text(colour = rep(c("red", "blue"), times=3)),
        # axis.ticks.x = element_blank(),
        axis.title  = element_text(size = 10, hjust = 0.5),
        panel.background = element_blank(),
        strip.background  = element_blank(),
        strip.text.y.left = element_text(angle = 0, hjust = 0),
        legend.position = "None")


z_limits <- range(c(dom_animals[[2]]$value, dom_animals[[2]]$value))


new_plot_1<-
ggplot(dom_animals[[1]], 
       aes(dom_animals_concern, 
           hum_liv_path_affect_wildlife, 
           fill= value)) + 
  likert_theme + 
  geom_tile() +
  scale_fill_gradient(low="white", high="blue") +
  labs(y = "Overall agreement with 'human and\nlivestock pathogens can impact wildlife health'\n", 
       x = "\nOverall agreement with 'Introduced domestic\nanimals are a concern'",
       title = "Domestic animals are not found in the protected area\n")


new_plot_1

# ggsave("submissions/Conservation_letters/RESPONSES_REVIEW_MAY_2024/plot_appendix_1.png",
#        plot = new_plot_1,
#        height = 8,
#        width = 13,
#        units = "in",
#        dpi = 600)  


```

```{r section 0.2 plot}
#| echo: false
#| message: false
#| warning: false
#| eval: true
#| fig-height: 3.5
#| fig-align: center
#| fig-cap: Figure S5. Distribution of protected area data managers responses across their overall agreement with 'human and livestock pathogens can impact wildlife health' and 'introduced domestic animals are a concern for the conservation goals of the protected area' for those protected area data managers that reported the presence of domestic animals in the protected area.

new_plot_2<-
  ggplot(dom_animals[[2]], 
         aes(dom_animals_concern, 
             hum_liv_path_affect_wildlife, 
             fill= value)) + 
  likert_theme + 
  geom_tile() +
  scale_fill_gradient(low="white", high="blue") +
  labs(y = "Overall agreement with 'human and\nlivestock pathogens can impact wildlife health'\n", 
       x = "\nOverall agreement with 'Introduced domestic\nanimals are a concern'",
       title = "Domestic animals are found in the protected area\n")

new_plot_2

# ggsave("submissions/Conservation_letters/RESPONSES_REVIEW_MAY_2024/plot_appendix_2.png",
#        plot = new_plot_2,
#        height = 8,
#        width = 13,
#        units = "in",
#        dpi = 600) 


```
